### 2022-03-21 manuscript.tex
p53figures [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/f639410c88922414b468ef64117835556bd27e8e.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/f639410c88922414b468ef64117835556bd27e8e/checks
https://github.com/scherzerthesis/thesis/actions/runs/2019171743

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/1a493f8ef1b1d34f03b4e1ee4cfd6e289b300a73/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/1a493f8ef1b1d34f03b4e1ee4cfd6e289b300a73}{scherzerthesis/thesis@1a493f8}
on March 21, 2022.

@@

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/f639410c88922414b468ef64117835556bd27e8e/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/f639410c88922414b468ef64117835556bd27e8e}{scherzerthesis/thesis@f639410}
on March 21, 2022.

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p53_1.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p53_2.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p53_3.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p53_4.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p53_5.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p536.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p537.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p538.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p539.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/p5310.png}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:04}
}
\end{figure}
